\plaintitle

### 2017-01-06 Paper/proceedings.tex
Changed keywords to semicolon delimited.
Fixed typos

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Regression by Eye: Estimating Trends\\in Bivariate Visualizations}
\def\plainauthor{Michael Correll and Jeffrey Heer}
\def\emptyauthor{}
\def\plainkeywords{Information Visualization, Graphical Perception, Regression}
\def\plaingeneralterms{Visualization}

@@

We investigated three types of common bivariate visualizations: scatter plots, line graphs, and area charts (see Fig. \ref{fig:types}). In each experiment, we presented participants with a visualization and asked them to interactively adjust trend lines to best fit the data.  Participants responded using a slider without tick marks, in order to limit anchoring effects~\cite{matejka2016effect}. Moving the slider adjusted a purple trend line by modifying its slope (in experiments 1 and 3) or its y-intercept (in experiment 2). Fig. \ref{fig:experiment} shows an example experimental task. After moving the slider, participants had to confirm their choice of trend line. The primary dependent measure is accuracy (e.g., the difference between the subject-specified slope and the slope of the series if the residuals were removed). We chose this design over a standard binary forced choice design for its greater expressiveness, as well as for the interactive feedback of adjusting the fit by hand. While other studies investigate the use of more expressive designs (such as free-form drawing)~\cite{kim2017}, we sought to disambiguate the model selection task (e.g., the selection of a a linear or non-linear model) from the model fitting task (adjusting the parameters of the selected model). Our design also reduces the impact of factors such as noise from motor movements or heterogeneous input devices.

@@

This work supported by a Moore Foundation Data-Driven Discovery Investigator Award.

>>>>

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Regression by Eye: Estimating Trends\\in Bivariate Visualizations}
\def\plainauthor{Michael Correll and Jeffrey Heer}
\def\emptyauthor{}
\def\plainkeywords{Information Visualization; Graphical Perception; Regression}
\def\plaingeneralterms{Visualization}

@@

We investigated three types of common bivariate visualizations: scatter plots, line graphs, and area charts (see Fig. \ref{fig:types}). In each experiment, we presented participants with a visualization and asked them to interactively adjust trend lines to best fit the data.  Participants responded using a slider without tick marks, in order to limit anchoring effects~\cite{matejka2016effect}. Moving the slider adjusted a purple trend line by modifying its slope (in experiments 1 and 3) or its y-intercept (in experiment 2). Fig. \ref{fig:experiment} shows an example experimental task. After moving the slider, participants had to confirm their choice of trend line. The primary dependent measure is accuracy (e.g., the difference between the subject-specified slope and the slope of the series if the residuals were removed). We chose this design over a standard binary forced choice design for its greater expressiveness, as well as for the interactive feedback of adjusting the fit by hand. While other studies investigate the use of more expressive designs (such as free-form drawing)~\cite{kim2017}, we sought to disambiguate the model selection task (e.g., the selection of a linear or non-linear model) from the model fitting task (adjusting the parameters of the selected model). Our design also reduces the impact of factors such as noise from motor movements or heterogeneous input devices.

@@

This work was supported by a Moore Foundation Data-Driven Discovery Investigator Award.
